The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-11-30 Paper.qmd
Moved code to analysis.R. Added numbers_to_words

```{r setup, include=FALSE}
source("analysisforpaper.R", local = knitr::knit_global())
library(modelsummary)
```

@@

`{r} dplyr::n_distinct(modeldf$householdID)` primary caretakers (females = `{r} table(caregivers$CaregiverSex)[1]`, males = `{r} table(caregivers$CaregiverSex)[2]`, non-binary = `{r} table(caregivers$CaregiverSex)[3]`) took the survey and provided signaling data for at least one child. `{r} nrow(modeldf)` children had frequency data for at least one signal, with `{r} nrow(modeldf_FULLSIG)` having data for all three. Among those with at least one record of signaling frequency, `{r} sex_table[1]` were female and `{r} sex_table[2]` were male. Anthropometric and signaling data exist for `{r} nrow(modeldf_FULLANTHROPOMETRICS)` children, of whom `{r} sex_table2[1]` were female and `{r} sex_table2[2]` were male. For summary statistics of study variables see @tbl-sumtab_combined and @tbl-sumtab_factors.

@@

@@

>>>>

```{r setup, include=FALSE}
source("analysis.R", local = knitr::knit_global())
```

@@

```{r}
sex_table <- table(modeldf$Sex)
```

`{r} xfun::numbers_to_words(n_distinct(modeldf$householdID), cap=T)` primary caretakers (females = `{r} table(caregivers$CaregiverSex)[1]`, males = `{r} table(caregivers$CaregiverSex)[2]`) took the survey and provided signaling data for at least one child. `{r} xfun::numbers_to_words(nrow(modeldf), cap=T)` children had frequency data for at least one signal, with `{r} nrow(modeldf_FULLSIG)` having data for all three. Among those with at least one record of signaling frequency, `{r} sex_table[1]` were female and `{r} sex_table[2]` were male. For summary statistics of study variables see @tbl-sumtab_combined and @tbl-sumtab_factors.

@@

```{r}
rel_need_table <- table(modeldf$RelativeNeed3)
```

@@

```{r}
response_overlap <- table(modeldf$PositiveResponse, modeldf$NegativeResponse)
```
